### 2019-03-13 _publications/jors/paper.tex
Fix TeX issues with JORS paper

%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.

\documentclass{jors}

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

\usepackage{biblatex}
\usepackage{hyperref}
\bibliography{paper}

\begin{document}

%% {\bf Software paper for submission to the Journal of Open Research Software} \\

%% To complete this template, please replace the blue text with your own. The paper has three main sections: (1) Overview; (2) Availability; (3) Reuse potential. \\

%% Please submit the completed paper to: editor.jors@ubiquitypress.com

%% \rule{\textwidth}{1pt}

\section*{(1) Overview}

\vspace{0.5cm}

\section*{Title}

PFHub: The Phase-Field Community Hub

\section*{Paper Authors}

1. Wheeler, Daniel; (corresponding author) 1\\
2. Keller, Trevor; 1\\
3. DeWitt, Stephen J.; 6\\
4. Jokisaari, Andrea M.; 5\\
5. Schwen, Daniel; 5\\
6. Guyer, Jonathan E.; 1\\
7. Aagesen, Larry; 5\\
8. Heinonen, Olle G.; 2\\
9. Voorhees, Peter W.; 4\\
10. Warren, James A.; 3

\section*{Paper Author Roles and Affiliations}

1. Materials Science and Engineering Division, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

2. Argonne National Laboratory, \\
Lemont, IL 60439 USA

3. Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology, \\
Gaithersburg, MD 20899 USA

4. Department of Materials Science and Engineering, \\
Northwestern University, \\
Evanston, IL 60208 USA

5. Fuel Modeling and Simulation Department, \\
Idaho National Laboratory, \\
Idaho Falls, ID 83415 USA

6. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

7. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

\section*{Abstract}

Scientific research communities often require an online portal to
summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An examplar of such a portal is $\mu$MAG~\cite{mumag}. The
reusable PFHub framework leverages existing online services to build a
static portal website that is considerably easier to deploy and
maintain without sacrificing content or scope. The first deployment of
the PFHub framework supports phase-field practitioners and code
developers participating in an effort to improve quality assurance for
phase-field codes.

\section*{Keywords}

\textcolor{blue}{keyword 1; keyword 2; etc. \\
Keywords should make it easy to identify who and what the software will be useful for.}

\section*{Introduction}

\textcolor{blue}{An overview of the software, how it was produced, and the research for which it has been used, including references to relevant research articles. A short comparison with software which implements similar functionality should be included in this section. }

\section*{Implementation and architecture}

\textcolor{blue}{How the software was implemented, with details of the architecture where relevant. Use of relevant diagrams is appropriate. Please also describe any variants and associated implementation differences.}

\section*{Quality control}

\textcolor{blue}{Detail the level of testing that has been carried out on the code (e.g. unit, functional, load etc.), and in which environments. If not already included in the software documentation, provide details of how a user could quickly understand if the software is working (e.g. providing examples of running the software with sample input and output data). }

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}

\textcolor{blue}{Please include minimum version compatibility.}

\section*{Programming language}

\textcolor{blue}{Please include minimum version compatibility.}

\section*{Additional system requirements}

\textcolor{blue}{E.g. memory, disk space, processor, input devices, output devices.}

\section*{Dependencies}

\textcolor{blue}{E.g. libraries, frameworks, incl. minimum version compatibility.}

\section*{List of contributors}

\textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}

\section*{Software location:}

{\bf Archive} \textcolor{blue}{(e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Publisher:]  \textcolor{blue}{Name of the person who deposited the software.}
	\item[Version published:] \textcolor{blue}{The version number of the software archived.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Code repository} \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Emulation environment} \textcolor{blue}{(if appropriate)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

\section*{Language}

\textcolor{blue}{Language of repository, software and supporting files.}

\section*{(3) Reuse potential}

\textcolor{blue}{Please describe in as much detail as possible the ways in which the software could be reused by other researchers both within and outside of your field. This should include the use cases for the software, and also details of how the software might be modified or extended (including how contributors should contact you) if appropriate. Also you must include details of what support mechanisms are in place for this software (even if there is no support).}

\section*{Acknowledgements}

\textcolor{blue}{Please add any relevant acknowledgements to anyone else who supported the project in which the software was created, but did not work directly on the software itself.}

\section*{Funding statement}

\textcolor{blue}{If the software resulted from funded research please give the funder and grant number.}

\section*{Competing interests}

\textcolor{blue}{If any of the authors have any competing interests then these must be declared. The authors’ initials should be used to denote differing competing interests. For example: “BH has minority shares in [company name], which part funded the research grant for this project. All other authors have no competing interests." \\
If there are no competing interests, please add the statement:
“The authors declare that they have no competing interests.” }

%% \section*{References}

\printbibliography

%% \textcolor{blue}{Please enter references in the Harvard style and include a DOI where available, citing them in the text with a number in square brackets, e.g. \\ }

%% \textcolor{blue}{[1] Piwowar, H A 2011 Who Shares? Who Doesn't? Factors Associated with Openly Archiving Raw Research Data. PLoS ONE 6(7): e18657. DOI: \\ http://dx.doi.org/10.1371/journal.pone.0018657.}

\vspace{2cm}

\rule{\textwidth}{1pt}

{ \bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

Authors retain copyright and grant the journal right of first publication with the work simultaneously licensed under a  \href{http://creativecommons.org/licenses/by/3.0/}{Creative Commons Attribution License} that allows others to share the work with an acknowledgement of the work's authorship and initial publication in this journal. \\

Authors are able to enter into separate, additional contractual arrangements for the non-exclusive distribution of the journal's published version of the work (e.g., post it to an institutional repository or publish it in a book), with an acknowledgement of its initial publication in this journal. \\

By submitting this paper you agree to the terms of this Copyright Notice, which will apply to this submission if and when it is published by this journal.

\end{document}

### 2019-03-13 _publications/jors/paper.tex
Sort out Makefile for latex build

@@
 
-\textcolor{blue}{keyword 1; keyword 2; etc. \\
-Keywords should make it easy to identify who and what the software will be useful for.}
+phase-field; materials-science; jekyll-website; reproducible-science
 
@@
 
-\textcolor{blue}{An overview of the software, how it was produced, and the research for which it has been used, including references to relevant research articles.
-A short comparison with software which implements similar functionality should be included in this section.
-}
+The phase-field method (PFM) describes material interfaces at the
+mesoscopic scale between atomic scale models and macroscale models.
+The PFM is well established and there are an assortment of code
+frameworks (*e.g.*, Moose~\cite{moose}, PRISMS-PF~\cite{prisms-pf},
+FiPy~\cite{fipy}, MMSP~\cite{mmsp}) available for solving the wide
+variety of phenomena associated with phase-field (*e.g.*, dendritic
+growth, spinodal decomposition, grain growth). However, phase-field
+research groups often develop codes in isolation and do not publish
+the code bases or do not support or distribute the code bases to the
+wider community. PFHub is a community effort spearheaded by the Center
+for Hierarchical Materials Design at Northwestern University and the
+National Institute of Standards and Technology to support the
+development of phase-field codes. The goal of PFHub is to improve
+cross-collaboration between phase-field code developers and
+practitioners by providing a standardized set of benchmark
+problems~\cite{bm1, bm2} along with a web framework for uploading and
+comparing benchmark results from different codes.
 

### 2019-03-13 _publications/jors/paper.tex
Working on JORS paper

@@
 \rhead{\footnotesize 3}
-\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
 
@@
 
+\usepackage{graphicx}
+\usepackage{hyperref}
+
 \begin{document}
 
+\newcommand\githublink[1]{\href{https://github.com/#1/}{\texttt{\textbf{@#1}}}}
 %% {\bf Software paper for submission to the Journal of Open Research Software} \\
@@
 
-1. Wheeler, Daniel; (corresponding author) 1\\
-2. Keller, Trevor; 1\\
-3. DeWitt, Stephen J.; 6\\
-4. Jokisaari, Andrea M.; 5\\
-5. Schwen, Daniel; 5\\
-6. Guyer, Jonathan E.; 1\\
-7. Aagesen, Larry; 5\\
-8. Heinonen, Olle G.; 2\\
-9. Voorhees, Peter W.; 4\\
-10. Warren, James A.; 3
+1. Wheeler, Daniel; (corresponding author) A\\
+2. Keller, Trevor; A\\
+3. DeWitt, Stephen J.; E\\
+4. Jokisaari, Andrea M.; D\\
+5. Schwen, Daniel; D\\
+6. Guyer, Jonathan E.; A\\
+7. Aagesen, Larry; D\\
+8. Heinonen, Olle G.; B\\
+9. Voorhees, Peter W.; C\\
+10. Warren, James A.; A
 
@@
 
-1. Materials Science and Engineering Division, \\
-Material Measurement Laboratory, \\
+A. Material Measurement Laboratory, \\
 National Institute of Standards and Technology,\\
@@
 
-2. Argonne National Laboratory, \\
+B. Argonne National Laboratory, \\
 Lemont, IL 60439 USA
 
-3. Laboratory Office, \\
-Material Measurement Laboratory, \\
-National Institute of Standards and Technology, \\
-Gaithersburg, MD 20899 USA
-
-4. Department of Materials Science and Engineering, \\
+C. Department of Materials Science and Engineering, \\
 Northwestern University, \\
@@
 
-5. Fuel Modeling and Simulation Department, \\
+D. Fuel Modeling and Simulation Department, \\
 Idaho National Laboratory, \\
@@
 
-6. Materials Science and Engineering Department, \\
+E. Materials Science and Engineering Department, \\
 University of Michigan, \\
@@
 
-7. Materials Science and Engineering Department, \\
+F. Materials Science and Engineering Department, \\
 University of Michigan, \\
@@
 The PFM is well established and there are an assortment of code
-frameworks (*e.g.*, Moose~\cite{moose}, PRISMS-PF~\cite{prisms-pf},
-FiPy~\cite{fipy}, MMSP~\cite{mmsp}) available for solving the wide
-variety of phenomena associated with phase-field (*e.g.*, dendritic
-growth, spinodal decomposition, grain growth). However, phase-field
-research groups often develop codes in isolation and do not publish
-the code bases or do not support or distribute the code bases to the
-wider community. PFHub is a community effort spearheaded by the Center
-for Hierarchical Materials Design at Northwestern University and the
-National Institute of Standards and Technology to support the
-development of phase-field codes. The goal of PFHub is to improve
-cross-collaboration between phase-field code developers and
-practitioners by providing a standardized set of benchmark
-problems~\cite{bm1, bm2} along with a web framework for uploading and
-comparing benchmark results from different codes.
+frameworks (\textit{e.g} Moose~\cite{moose},
+PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
+available for solving the wide variety of phenomena associated with
+phase-field (\textit{e.g.} dendritic growth, spinodal decomposition,
+grain growth). However, phase-field research groups often develop
+codes in isolation and do not publish the code bases or do not support
+or distribute the code bases to the wider community. PFHub is a
+community effort spearheaded by the Center for Hierarchical Materials
+Design at Northwestern University and the National Institute of
+Standards and Technology to support the development of phase-field
+codes. The goal of PFHub is to improve cross-collaboration between
+phase-field code developers and practitioners by providing a
+standardized set of benchmark problems~\cite{bm1, bm2} along with a
+web framework for uploading and comparing benchmark results from
+different codes.
 
@@
 
-\textcolor{blue}{How the software was implemented, with details of the architecture where relevant.
-Use of relevant diagrams is appropriate.
-Please also describe any variants and associated implementation differences.}
+The PFHub website provides a facility for uploading, displaying and
+comparing results from the benchmark problems. The website uses the
+Jekyll static website generator along with automated frontend
+processing to eliminate the need for content management
+systems~\cite{cmsfree}, which are generally costly to maintain
+especially for small scientific communities with limited funding and
+manpower.
+
+The workflow for uploading benchmark results relies on third party
+tools using the following steps, illustrated in
+Figure~\ref{fig:pfhub_website}.
+
+\begin{itemize}
+  \item The users are first required to archive simulation outputs at
+    an archival resource (\textit{e.g.} Figshare) configured with
+    permissive cross-origin resource sharing (CORS).
+  \item The metadata summarizing each simulation is entered into a
+    form on the website, including relevant details such as memory
+    usage, run time and links to the data archived in the first step.
+  \item Upon submission, the Staticman app~\cite{staticman} submits
+    the entered metadata as a GitHub pull request to the PFHub GitHub
+    repository.  The metadata is stored in a YAML file with a unique
+    path in the repository.
+  \item Travis CI~\cite{travis} performs linting on the submission and
+    then launches a new version of the website using
+    Surge~\cite{surge}. The PFHub admins can then examine the new
+    submission and further changes can be made if necessary.
+  \item Once review has been completed to the satisfaction of both the
+    uploading scientist and the website maintainers, the pull request
+    is merged and served to the World Wide Web using a hosting service
+    compatible with GitHub Pages.
+\end{itemize}
+
+A combination of Jekyll templates and Coffeescript is used to access
+and download the data links in the submitted YAML files and then
+display the data in interactive figures on the website. The
+combination of a central repository on GitHub for website source code
+and metadata with distributed data records on third-party archives
+avoids the complexity and administrative overhead of maintaining a
+live database and associated backend app. The PFHub infrastructure
+provides a template for other small scientific communities to host
+custom content and integrate data from members of their community.
+
+\begin{figure}
+  \includegraphics[width=4in]{pfhub_website.png}
+  \caption{Schematic overview of the PFHub framework for building
+    scientific research portals, simply.}
+  \centering
+  \label{fig:pfhub_website}
+\end{figure}
 
@@
 
-\textcolor{blue}{Detail the level of testing that has been carried out on the code (e.g.
-unit, functional, load etc.), and in which environments.
-If not already included in the software documentation, provide details of how a user could quickly understand if the software is working (e.g.
-providing examples of running the software with sample input and output data).
-}
+Every pull request to the repository is tested using Travis CI. The
+full test recipe is outlined in the \texttt{.travis.yml} file
+available in the repository~\cite{travisyml}. The entire framework is
+built using the Nix Package Manager~\cite{nix} and pinned to a
+specific version of the Nixpkgs repository. Using Nix ensures the
+development and automated testing environments are identical. PFHub is
+built using both Python and Coffeescript code so test and lint
+frameworks dedicated to both of those languages are used. Furthermore,
+Surge~\cite{surge} is used to display the final website link in the
+pull request so that reviewers can look at a visual display of the
+website before merging.
 
@@
 
-\textcolor{blue}{Please include minimum version compatibility.}
+PFHub can be deployed on any platform supporting Nix, which includes
+all contemporary Linux and Mac OS X platforms.
 
@@
 
-\textcolor{blue}{Please include minimum version compatibility.}
+PFHub is currently build and tested using the programming language and
+versions outlined in Table~\ref{tab:versions}.
+
+\begin{table}[h!]
+  \centering
+  \begin{tabular}{|l|l|}
+    \hline
+    Language         & Version \\
+    \hline
+    HTML             & 5       \\
+    Jupyter Notebook & 5.4.0   \\
+    JavaScript       & 5       \\
+    Nix              & 2.1.3   \\
+    CoffeeScript     & 1.12.7  \\
+    CSS              & 4       \\
+    \hline
+  \end{tabular}
+  \caption{PFHub programming languages and corresponding supported
+    versions.}
+  \label{tab:versions}
+\end{table}
 
@@
 
-\textcolor{blue}{E.g. memory, disk space, processor, input devices, output devices.}
+There are no additionial system requirements.
 
@@
 
-\textcolor{blue}{E.g. libraries, frameworks, incl. minimum version compatibility.}
+The entire environment can be built using Nix so the only required
+dependency is a functional Nix installation.
 
@@
 
-\textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}
+1. Wheeler, Daniel; A, \githublink{wd15} \\
+2. Keller, Trevor; A, \githublink{tkphd} \\
+3. DeWitt, Stephen J.; E, \githublink{stvdwtt} \\
+4. Jokisaari, Andrea M.; D, \githublink{amjokisaari} \\
+5. Schwen, Daniel; D, \githublink{dschwen} \\
+6. Guyer, Jonathan E.; A, \githublink{guyer} \\
+
+See the contributors list on GitHub~\cite{contributors}.
 
@@
 
-{\bf Archive} \textcolor{blue}{(e.g.
-institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)}
+{\bf Archive}
 
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Publisher:]  \textcolor{blue}{Name of the person who deposited the software.}
-	\item[Version published:] \textcolor{blue}{The version number of the software archived.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
+	\item[Name:] Zenodo
+	\item[Persistent identifier:] 10.5281/zenodo.2592705
+	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
+	\item[Publisher:]  Daniel Wheeler
+	\item[Version published:] v0.1
+	\item[Date published:] 13/03/19
 \end{description}
 
-{\bf Code repository} \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}
+{\bf Code repository}
 
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
+	\item[Name:] GitHub
+	\item[Persistent identifier:] 10.5281/zenodo.2592705
+	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
+	\item[Date published:] 13/03/19
 \end{description}
 
-{\bf Emulation environment} \textcolor{blue}{(if appropriate)}
+\section*{Languages}
 
-\begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
-\end{description}
-
-\section*{Language}
-
-\textcolor{blue}{Language of repository, software and supporting files.}
+English
 
@@
 
-\textcolor{blue}{If any of the authors have any competing interests then these must be declared.
-The authors’ initials should be used to denote differing competing interests.
-For example: “BH has minority shares in [company name], which part funded the research grant for this project.
-All other authors have no competing interests." \\
-If there are no competing interests, please add the statement:
-“The authors declare that they have no competing interests.” }
+The authors declare that they have no competing interests.
 

### 2019-03-14 _publications/jors/paper.tex
more changes

@@
 9. Voorhees, Peter W.; C\\
-10. Warren, James A.; A
+10. Warren, James A.; G
 
@@
 
-A. Material Measurement Laboratory, \\
+A. Materials Science and Engineering Division, \\
+Material Measurement Laboratory, \\
 National Institute of Standards and Technology,\\
@@
 
+G. Material Measurement Laboratory Office, \\
+Material Measurement Laboratory, \\
+National Institute of Standards and Technology,\\
+Gaithersburg, MD 20899 USA
+
 \section*{Abstract}
@@
 present a quantitative comparison of past attempts in a compelling
-way. An examplar of such a portal is $\mu$MAG~\cite{mumag}. The
+way. An exemplar of such a portal is $\mu$MAG~\cite{mumag}. The
 reusable PFHub framework leverages existing online services to build a
@@
 The PFM is well established and there are an assortment of code
-frameworks (\textit{e.g} Moose~\cite{moose},
+frameworks (\emph{e.g} Moose~\cite{moose},
 PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
 available for solving the wide variety of phenomena associated with
-phase-field (\textit{e.g.} dendritic growth, spinodal decomposition,
+phase-field (\emph{e.g.} dendritic growth, spinodal decomposition,
 grain growth). However, phase-field research groups often develop
@@
 comparing results from the benchmark problems. The website uses the
-Jekyll static website generator along with automated frontend
-processing to eliminate the need for content management
+Jekyll static website generator~\cite{jekyll} along with automated
+frontend processing to eliminate the need for content management
 systems~\cite{cmsfree}, which are generally costly to maintain
@@
   \item The users are first required to archive simulation outputs at
-    an archival resource (\textit{e.g.} Figshare) configured with
+    an archival resource (\emph{e.g.} Figshare) configured with
     permissive cross-origin resource sharing (CORS).
@@
 
-A combination of Jekyll templates and Coffeescript is used to access
+A combination of Jekyll templates and Coffeescript are used to access
 and download the data links in the submitted YAML files and then
@@
 
-Every pull request to the repository is tested using Travis CI. The
-full test recipe is outlined in the \texttt{.travis.yml} file
-available in the repository~\cite{travisyml}. The entire framework is
-built using the Nix Package Manager~\cite{nix} and pinned to a
-specific version of the Nixpkgs repository. Using Nix ensures the
-development and automated testing environments are identical. PFHub is
-built using both Python and Coffeescript code so test and lint
-frameworks dedicated to both of those languages are used. Furthermore,
-Surge~\cite{surge} is used to display the final website link in the
-pull request so that reviewers can look at a visual display of the
-website before merging.
+The framework has a fully automated test recipe deployed on Travis CI
+with an environment built using the Nix Package
+Manager~\cite{nix}. The environment is pinned to a specific version of
+the Nixpkgs repository ensuring fully reproducible build and test
+phases as well as ensuring that the development and automated testing
+environments are identical. The full test recipe is outlined in a
+\texttt{.travis.yml} file stored in the repository~\cite{travisyml}
+and consists of the following steps.
+
+\begin{itemize}
+  \item Build the Nix environment from a cached storage reducing the
+    build time.
+  \item Run automated tests on Jupyter Notebooks using
+    NBval~\cite{nbval} and Py.test~\cite{pytest}.
+  \item Lint and test front-end Coffeescript using appropriate tools.
+  \item Display a temporary version of the website using
+    Surge~\cite{surge} for visual review.
+\end{itemize}
 
@@
 
-PFHub can be deployed on any platform supporting Nix, which includes
-all contemporary Linux and Mac OS X platforms.
+The PFHub framework can be deployed on any platform supporting Nix,
+which includes all contemporary Linux and Mac OS X platforms. However,
+since the framework is built with Jekyll and automated front-end
+processing it can be deployed on GitHub's Pages infrastructure.
 
@@
 
-PFHub is currently build and tested using the programming language and
+PFHub is currently built and tested using the programming language and
 versions outlined in Table~\ref{tab:versions}.
@@
   \centering
+  \caption{PFHub programming languages and corresponding supported
+    versions.}
   \begin{tabular}{|l|l|}
@@
   \end{tabular}
-  \caption{PFHub programming languages and corresponding supported
-    versions.}
   \label{tab:versions}
@@
 
-There are no additionial system requirements.
+There are no additional system requirements.
 
@@
 
-The entire environment can be built using Nix so the only required
-dependency is a functional Nix installation.
+The entire environment can be built using the Nix Package Manager so
+the only required dependency is a functional Nix installation. The
+full set of dependencies are extensive and fully outlined in the Nix
+recipe stored in the repository~\cite{nix-recipe}.
 
@@
 	\item[Name:] Zenodo
-	\item[Persistent identifier:] 10.5281/zenodo.2592705
-	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
+	\item[Persistent identifier:]
+          \href{https://dx.doi.org/10.5281/zenodo.2592705}{10.5281/zenodo.2592705}
+	\item[Licence:] NIST Software License~\cite{nistlicense}
 	\item[Publisher:]  Daniel Wheeler
@@
 	\item[Name:] GitHub
-	\item[Persistent identifier:] 10.5281/zenodo.2592705
+	\item[Persistent identifier:] \url{https://github.com/usnistgov/pfhub/tree/v0.1}
 	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
@@
 
-\textcolor{blue}{Please describe in as much detail as possible the ways in which the software could be reused by other researchers both within and outside of your field.
-This should include the use cases for the software, and also details of how the software might be modified or extended (including how contributors should contact you) if appropriate.
-Also you must include details of what support mechanisms are in place for this software (even if there is no support).}
+\textcolor{blue}{Please describe in as much detail as possible the
+  ways in which the software could be reused by other researchers both
+  within and outside of your field. This should include the use cases
+  for the software, and also details of how the software might be
+  modified or extended (including how contributors should contact you)
+  if appropriate. Also you must include details of what support
+  mechanisms are in place for this software (even if there is no
+  support).}
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
-\textcolor{blue}{Please add any relevant acknowledgements to anyone else who supported the project in which the software was created, but did not work directly on the software itself.}
+\textcolor{blue}{Please add any relevant acknowledgments to anyone
+  else who supported the project in which the software was created,
+  but did not work directly on the software itself.}
 
@@
 
-\textcolor{blue}{If the software resulted from funded research please give the funder and grant number.}
+\textcolor{blue}{If the software resulted from funded research please
+  give the funder and grant number.}
 

### 2019-03-14 _publications/jors/paper.tex
Fix e.g. comma issue

@@
 The PFM is well established and there are an assortment of code
-frameworks (\emph{e.g} Moose~\cite{moose},
+frameworks (\emph{e.g.}, Moose~\cite{moose},
 PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
 available for solving the wide variety of phenomena associated with
-phase-field (\emph{e.g.} dendritic growth, spinodal decomposition,
+phase-field (\emph{e.g.}, dendritic growth, spinodal decomposition,
 grain growth). However, phase-field research groups often develop
@@
   \item The users are first required to archive simulation outputs at
-    an archival resource (\emph{e.g.} Figshare) configured with
+    an archival resource (\emph{e.g.}, Figshare) configured with
     permissive cross-origin resource sharing (CORS).

### 2019-03-14 _publications/jors/paper.tex
more changes
Copy of paper ready for Trevor

@@
 PFHub: The Phase-Field Community Hub
+
+\url{https://pages.nist.gov/pfhub}
 
@@
     NBval~\cite{nbval} and Py.test~\cite{pytest}.
+  \item Run validation tests on HTML files using
+    HTMLProofer~\cite{htmlproofer}.
   \item Lint and test front-end Coffeescript using appropriate tools.
@@
 	\item[Persistent identifier:] \url{https://github.com/usnistgov/pfhub/tree/v0.1}
-	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
+	\item[Licence:] NIST Software License~\cite{nistlicense}
 	\item[Date published:] 13/03/19
@@
 
-\textcolor{blue}{Please describe in as much detail as possible the
-  ways in which the software could be reused by other researchers both
-  within and outside of your field. This should include the use cases
-  for the software, and also details of how the software might be
-  modified or extended (including how contributors should contact you)
-  if appropriate. Also you must include details of what support
-  mechanisms are in place for this software (even if there is no
-  support).}
+The website infrastructure can be forked and deployed with minimum
+effort including the upload mechanism using Staticman. However,
+customizing the website for a particular scientific community would
+require considerable effort. The following steps are the more
+challenging aspects of deploying the framework for a new community.
+
+\begin{itemize}
+  \item Edit or upload new Jupyter Notebooks with benchmark or data
+    requirement descriptions.
+  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
+    upload requirements and describe the figures that need to be
+    generated on the upload comparison pages.
+  \item Edit the \texttt{\_config.yml} file to update links and text
+    related to the configuration for all aspects of the website.
+  \item Update Markdown files to reflect the new content and mission
+    of the scientific community.
+  \item Remove data and files that are not required by the new
+    community.
+\end{itemize}
+
+Currently, a deployment for a new community has not been attempted
+and, thus, the above steps need to be refined and documented.
 
@@
 
-\textcolor{blue}{Please add any relevant acknowledgments to anyone
-  else who supported the project in which the software was created,
-  but did not work directly on the software itself.}
+We gratefully acknowledge input and guidance from all participants in
+the series of Phase-Field workshops held between 2015 and 2018 at the
+Center for Hierarchical Material Design~\cite{workshops}.
 
@@
 
-\textcolor{blue}{If the software resulted from funded research please
-  give the funder and grant number.}
+Ask Jim for this text.
 

### 2019-03-18 _data/hexbin.py
Remove progressbar2 as it breaks some Nix builds
Address #945

Debian Nix builds are breaking with progressbar2, but it isn't
required for anything important. hexbin.py has been modified not to
use it.

@@ -3,6 +3,7 @@
 
 import itertools
 from random import shuffle
+import sys
 
 import json
 import io
@@ -10,7 +11,6 @@ import urllib
 
 import yaml
 from PIL import Image
-import progressbar
 import requests
 
 
@@ -67,23 +67,14 @@ def thumbnail_image(image_url, size):
 def hexbin_image(data, x_size, y_size, ni_count, nj_count):
     """Build the combined thumbnails
     """
-    widgets = [
-        progressbar.Percentage(),
-        " ",
-        progressbar.Bar(marker=progressbar.RotatingMarker()),
-        " ",
-        progressbar.ETA(),
-    ]
-
-    pbar = progressbar.ProgressBar(widgets=widgets, maxval=len(data)).start()
+    image_count = len(data)
 
     for counter, datum in enumerate(data):
         image_url = datum["image"]
         image = thumbnail_image(image_url, (x_size, y_size))
         datum["thumbnail"] = image
-        pbar.update(counter + 1)
-
-    pbar.finish()
+        sys.stdout.write(f"\rProgress: {counter} / {image_count}")
+        sys.stdout.flush()
 
     blank_image = Image.new(
         "RGB", (x_size * nj_count, y_size * ni_count), (255, 255, 255, 0)

### 2019-03-19 _publications/jors/paper.tex
Add funding statement
Update for tkphd review

@@
 
-\section*{Title}
-
-PFHub: The Phase-Field Community Hub
-
+\section{Title}
+\par\bigskip
+PFHub: The Phase-Field Community Hub\\[\baselineskip]
 \url{https://pages.nist.gov/pfhub}
@@
 the only required dependency is a functional Nix installation. The
-full set of dependencies are extensive and fully outlined in the Nix
-recipe stored in the repository~\cite{nix-recipe}.
+PFHub framework has over 2000 separate package dependencies using
+data from the Nix package manager. The full dependency graph for PFHub
+can be seen online~\cite{dependencies}.
 
@@
 
-Ask Jim for this text.
+D.W. wishes to acknowledge the Materials Genome Initiative funding
+allocated to the National Institute of Standards and Technology.
 

### 2019-03-19 _publications/jors/paper.tex
Update for tkphd review

@@
 
-\section{Title}
+\section*{Title}
 \par\bigskip
@@
 present a quantitative comparison of past attempts in a compelling
-way. An exemplar of such a portal is $\mu$MAG~\cite{mumag}. The
-reusable PFHub framework leverages existing online services to build a
-static portal website that is considerably easier to deploy and
-maintain without sacrificing content or scope. The first deployment of
-the PFHub framework supports phase-field practitioners and code
-developers participating in an effort to improve quality assurance for
+way. An exemplar of such a portal is
+$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
+  instruments, or materials (or suppliers, or software, ...) are
+  identified in this paper to foster understanding. Such
+  identification does not imply recommendation or endorsement by the
+  National Institute of Standards and Technology, nor does it imply
+  that the materials or equipment identified are necessarily the best
+  available for the purpose.\label{disclaimer}}. The reusable PFHub
+framework leverages existing online services to build a static portal
+website that is considerably easier to deploy and maintain without
+sacrificing content or scope. The first deployment of the PFHub
+framework supports phase-field practitioners and code developers
+participating in an effort to improve quality assurance for
 phase-field codes.
@@
 frameworks (\emph{e.g.}, Moose~\cite{moose},
-PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
-available for solving the wide variety of phenomena associated with
-phase-field (\emph{e.g.}, dendritic growth, spinodal decomposition,
-grain growth). However, phase-field research groups often develop
-codes in isolation and do not publish the code bases or do not support
-or distribute the code bases to the wider community. PFHub is a
+PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
+MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
+solving the wide variety of phenomena associated with phase-field
+(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
+growth). However, phase-field research groups often develop codes in
+isolation and do not publish the code bases or do not support or
+distribute the code bases for the wider community. PFHub is a
 community effort spearheaded by the Center for Hierarchical Materials
 Design at Northwestern University and the National Institute of
-Standards and Technology to support the development of phase-field
-codes. The goal of PFHub is to improve cross-collaboration between
-phase-field code developers and practitioners by providing a
-standardized set of benchmark problems~\cite{bm1, bm2} along with a
-web framework for uploading and comparing benchmark results from
-different codes.
+Standards and Technology to support the development of phase field
+codes. In particular, the PFHub effort focuses on improving
+cross-collaboration between phase-field code developers and
+practitioners by providing a standardized set of benchmark
+problems~\cite{bm1, bm2} along with a web framework for uploading and
+comparing benchmark results from different codes.
 
@@
 \begin{itemize}
-  \item The users are first required to archive simulation outputs at
+  \item The users are first required to upload simulation outputs to
     an archival resource (\emph{e.g.}, Figshare) configured with
@@
   \item Travis CI~\cite{travis} performs linting on the submission and
-    then launches a new version of the website using
+    then launches a temporary version of the proposed website using
     Surge~\cite{surge}. The PFHub admins can then examine the new
@@
 avoids the complexity and administrative overhead of maintaining a
-live database and associated backend app. The PFHub infrastructure
-provides a template for other small scientific communities to host
-custom content and integrate data from members of their community.
+live database and associated back-end application. The PFHub
+infrastructure provides a template for other small scientific
+communities to host custom content and integrate data from members of
+their community.
 
 \begin{figure}
-  \includegraphics[width=4in]{pfhub_website.png}
+  \includegraphics[width=\textwidth]{pfhub_website.png}
   \caption{Schematic overview of the PFHub framework for building
@@
 
-PFHub is currently built and tested using the programming language and
-versions outlined in Table~\ref{tab:versions}.
+PFHub is currently built and tested using the programming languages
+and versions outlined in Table~\ref{tab:versions}.
 
@@
 
-The website infrastructure can be forked and deployed with minimum
-effort including the upload mechanism using Staticman. However,
-customizing the website for a particular scientific community would
-require considerable effort. The following steps are the more
-challenging aspects of deploying the framework for a new community.
+The website infrastructure can be cloned as a Git repository or
+downloaded as a ZIP archive and deployed with minimum effort. The
+mechanism for uploading data using Staticman can be easily configured
+for a new repository location. However, customizing the content of the
+website for a particular scientific community would require
+considerable effort. The following steps are the more challenging
+aspects of deploying the framework for a new community.
 
 \begin{itemize}
-  \item Edit or upload new Jupyter Notebooks with benchmark or data
-    requirement descriptions.
+  \item Upload new benchmark defintions in a format that Jekyll can
+    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
   \item Edit the \texttt{benchmarks.yaml} file to reflect the new
@@
 
-%% \section*{References}
-
 \printbibliography
 
-%% \textcolor{blue}{Please enter references in the Harvard style and include a DOI where available, citing them in the text with a number in square brackets, e.g. \\ }
-
-%% \textcolor{blue}{[1] Piwowar, H A 2011 Who Shares?
-Who Doesn't?
-Factors Associated with Openly Archiving Raw Research Data.
-PLoS ONE 6(7): e18657.
-DOI: \\ http://dx.doi.org/10.1371/journal.pone.0018657.}
-
-\vspace{2cm}
-
-\rule{\textwidth}{1pt}
-
-{ \bf Copyright Notice} \\
-Authors who publish with this journal agree to the following terms: \\
-
-Authors retain copyright and grant the journal right of first publication with the work simultaneously licensed under a  \href{http://creativecommons.org/licenses/by/3.0/}{Creative Commons Attribution License} that allows others to share the work with an acknowledgement of the work's authorship and initial publication in this journal.
-\\
-
-Authors are able to enter into separate, additional contractual arrangements for the non-exclusive distribution of the journal's published version of the work (e.g., post it to an institutional repository or publish it in a book), with an acknowledgement of its initial publication in this journal.
-\\
-
-By submitting this paper you agree to the terms of this Copyright Notice, which will apply to this submission if and when it is published by this journal.
-
 \end{document}

### 2019-03-20 _publications/jors/paper.tex
Add Tonks as author
Update for stvdwtt review

@@
 \renewcommand\headrule{}
-\rhead{\footnotesize 3}
 
@@
 \usepackage{hyperref}
+
+\setlength{\parskip}{\baselineskip}%
+\setlength{\parindent}{0pt}%
 
@@
 8. Heinonen, Olle G.; B\\
-9. Voorhees, Peter W.; C\\
-10. Warren, James A.; G
+9. Tonks, Michael R.; G\\
+10. Voorhees, Peter W.; C\\
+11. Warren, James A.; F
 
@@
 
-F. Materials Science and Engineering Department, \\
-University of Michigan, \\
-Ann Arbor, MI 48109 USA
-
-G. Material Measurement Laboratory Office, \\
+F. Material Measurement Laboratory Office, \\
 Material Measurement Laboratory, \\
@@
 
+G. Department of Materials Science and Engineering, \\
+University of Florida, \\
+Gainesville, FL 32611
+
 \section*{Abstract}
 
-Scientific research communities often require an online portal to
-summarize a shared challenge, collect attempts at a solution, and
+An online portal provides a valuable space for scientific communities
+to summarize a shared challenge, collect attempts at a solution, and
 present a quantitative comparison of past attempts in a compelling
@@
 The PFM is well established and there are an assortment of code
-frameworks (\emph{e.g.}, Moose~\cite{moose},
+frameworks (\emph{e.g.}, MOOSE~\cite{moose},
 PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
 MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
-solving the wide variety of phenomena associated with phase-field
+solving the wide variety of phenomena associated with the PFM
 (\emph{e.g.}, dendritic growth, spinodal decomposition, grain
 growth). However, phase-field research groups often develop codes in
-isolation and do not publish the code bases or do not support or
-distribute the code bases for the wider community. PFHub is a
-community effort spearheaded by the Center for Hierarchical Materials
-Design at Northwestern University and the National Institute of
-Standards and Technology to support the development of phase field
-codes. In particular, the PFHub effort focuses on improving
-cross-collaboration between phase-field code developers and
-practitioners by providing a standardized set of benchmark
-problems~\cite{bm1, bm2} along with a web framework for uploading and
-comparing benchmark results from different codes.
+isolation and do not support or distribute the code bases to the wider
+community. PFHub is a community effort spearheaded by the Center for
+Hierarchical Materials Design at Northwestern University and the
+National Institute of Standards and Technology to support the
+development of phase-field codes. In particular, the PFHub effort
+focuses on improving cross-collaboration between phase-field code
+developers and practitioners by providing a standardized set of
+benchmark problems~\cite{bm1, bm2} along with a web framework for
+uploading and comparing benchmark results from different codes.
 
@@
 especially for small scientific communities with limited funding and
-manpower.
+staffing.
 
@@
 and download the data links in the submitted YAML files and then
-display the data in interactive figures on the website. The
-combination of a central repository on GitHub for website source code
-and metadata with distributed data records on third-party archives
-avoids the complexity and administrative overhead of maintaining a
-live database and associated back-end application. The PFHub
-infrastructure provides a template for other small scientific
+display the data in interactive plots on the website.  Previous
+iterations of PFHub used the Vega JSON Library~\cite{vega} to generate
+the interactive plots, but now the Plotly JavaScript Graphing
+Library~\cite{plotly} is used exclusively as it provides a more
+programmable interface and requires less upfront configuration.
+
+The benchmark specifications consist of equations, narrative, plots
+and code samples; and are composed in Jupyter Notbooks. The Jupyter
+Notebooks are included as static objects in the website after
+translation into HTML using the nbconvert tool~\cite{jupyter}.
+
+The combination of a central repository on GitHub for website source
+code and metadata with distributed data records on third-party
+archives avoids the complexity and administrative overhead of
+maintaining a live database and associated back-end application. The
+PFHub infrastructure provides a template for other small scientific
 communities to host custom content and integrate data from members of
@@
 The PFHub framework can be deployed on any platform supporting Nix,
-which includes all contemporary Linux and Mac OS X platforms. However,
-since the framework is built with Jekyll and automated front-end
-processing it can be deployed on GitHub's Pages infrastructure.
+which includes all contemporary Linux and Mac OS X platforms. Since
+the framework is built with Jekyll and automated front-end processing,
+it can be deployed on GitHub's Pages infrastructure, which enables
+streamlined deployment without the need for any back-end
+infrastructure.
 
@@
 \begin{itemize}
-  \item Upload new benchmark defintions in a format that Jekyll can
+  \item Upload new benchmark definitions in a format that Jekyll can
     parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
@@
 D.W. wishes to acknowledge the Materials Genome Initiative funding
-allocated to the National Institute of Standards and Technology.
+allocated to the National Institute of Standards and Technology. S.J.D
+wishes to acknowledge funding from the U.S. Department of Energy,
+Office of Basic Energy Sciences, Division of Materials Sciences and
+Engineering under Award \#DE-SC0008637 as part of the Center for
+PRedictive Integrated Structural Materials Science (PRISMS Center) at
+University of Michigan.
 

### 2019-03-22 _publications/jors/paper.tex
Update for tphd and guyer reviews

@@
 way. An exemplar of such a portal is
-$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
-  instruments, or materials (or suppliers, or software, ...) are
-  identified in this paper to foster understanding. Such
-  identification does not imply recommendation or endorsement by the
-  National Institute of Standards and Technology, nor does it imply
-  that the materials or equipment identified are necessarily the best
-  available for the purpose.\label{disclaimer}}. The reusable PFHub
+$\mu$MAG~\cite{mumag}. The reusable PFHub
 framework leverages existing online services to build a static portal
@@
 phase-field codes.
+
+%% ~\footnote{Certain commercial equipment,
+%%   instruments, or materials (or suppliers, or software, ...) are
+%%   identified in this paper to foster understanding. Such
+%%   identification does not imply recommendation or endorsement by the
+%%   National Institute of Standards and Technology, nor does it imply
+%%   that the materials or equipment identified are necessarily the best
+%%   available for the purpose.\label{disclaimer}}
+
+%% ~\textsuperscript{\ref{disclaimer}}
 
@@
 PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
-MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
-solving the wide variety of phenomena associated with the PFM
-(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
-growth). However, phase-field research groups often develop codes in
-isolation and do not support or distribute the code bases to the wider
-community. PFHub is a community effort spearheaded by the Center for
-Hierarchical Materials Design at Northwestern University and the
-National Institute of Standards and Technology to support the
-development of phase-field codes. In particular, the PFHub effort
-focuses on improving cross-collaboration between phase-field code
-developers and practitioners by providing a standardized set of
-benchmark problems~\cite{bm1, bm2} along with a web framework for
-uploading and comparing benchmark results from different codes.
+MMSP~\cite{mmsp}) available for
+solving the wide variety of mesoscale phenomena (\emph{e.g.},
+dendritic growth, spinodal decomposition, grain growth). However,
+phase-field research groups often develop codes in isolation and do
+not support or distribute the code bases to the wider community. PFHub
+is a community effort spearheaded by the Center for Hierarchical
+Materials Design at Northwestern University and the National Institute
+of Standards and Technology to support the development of phase-field
+codes. In particular, the PFHub effort focuses on improving
+cross-collaboration between phase-field code developers and
+practitioners by providing a standardized set of benchmark
+problems~\cite{bm1, bm2} along with a web framework for uploading and
+comparing benchmark results from different codes.
 
@@
   \item The users are first required to upload simulation outputs to
-    an archival resource (\emph{e.g.}, Figshare) configured with
-    permissive cross-origin resource sharing (CORS).
+    an archival resource (\emph{e.g.}, Figshare~\footnote{Certain
+      commercial equipment, instruments, or materials (or suppliers,
+      or software, ...) are identified in this paper to foster
+      understanding. Such identification does not imply recommendation
+      or endorsement by the National Institute of Standards and
+      Technology, nor does it imply that the materials or equipment
+      identified are necessarily the best available for the
+      purpose.\label{disclaimer}}) configured with permissive
+    cross-origin resource sharing (CORS).
   \item The metadata summarizing each simulation is entered into a
@@
 and download the data links in the submitted YAML files and then
-display the data in interactive plots on the website.  Previous
-iterations of PFHub used the Vega JSON Library~\cite{vega} to generate
-the interactive plots, but now the Plotly JavaScript Graphing
-Library~\cite{plotly} is used exclusively as it provides a more
-programmable interface and requires less upfront configuration.
+display the data in interactive plots on the website. The interactive
+plots are displayed using the Plotly JavaScript Graphing
+Library~\cite{plotly} as it provides a programmable interface and
+requires minimal configuration.
 
 The benchmark specifications consist of equations, narrative, plots
-and code samples; and are composed in Jupyter Notbooks. The Jupyter
+and code samples, and are composed in Jupyter Notebooks. The Jupyter
 Notebooks are included as static objects in the website after

### 2019-03-26 _publications/jors/paper.tex
Update abstract with @amjokisaari changes
Tried to incorporate @amjokosaari changes, but also keep the abstract
at ~100 words, which is a hard requirement from the journal. The new
abstract is ~110 words. The @amjokosaari version of the abstract was
~130 words, which is probably too many.

@@
 
-An online portal provides a valuable space for scientific communities
-to summarize a shared challenge, collect attempts at a solution, and
-present a quantitative comparison of past attempts in a compelling
-way. An exemplar of such a portal is
-$\mu$MAG~\cite{mumag}. The reusable PFHub
-framework leverages existing online services to build a static portal
-website that is considerably easier to deploy and maintain without
-sacrificing content or scope. The first deployment of the PFHub
-framework supports phase-field practitioners and code developers
-participating in an effort to improve quality assurance for
-phase-field codes.
-
-%% ~\footnote{Certain commercial equipment,
-%%   instruments, or materials (or suppliers, or software, ...) are
-%%   identified in this paper to foster understanding. Such
-%%   identification does not imply recommendation or endorsement by the
-%%   National Institute of Standards and Technology, nor does it imply
-%%   that the materials or equipment identified are necessarily the best
-%%   available for the purpose.\label{disclaimer}}
-
-%% ~\textsuperscript{\ref{disclaimer}}
+Scientific communities struggle with the challenge of effectively and
+efficiently sharing content and data. An online portal provides a
+valuable space for scientific communities to discuss challenges and
+collate scientific results. Examples of such portals include the
+Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
+Potentials Repository (IPR~\cite{}) and on a larger scale the NIH
+Genetic Sequence Database (GenBank~\cite{}). In this work, we present
+a description of a generic web portal that leverages existing online
+services to provide a framework that may be adopted by other
+scientific communities. The first deployment of the PFHub framework
+supports phase-field practitioners and code developers participating
+in an effort to improve quality assurance for phase-field codes.
 

### 2019-03-26 _publications/jors/paper.tex
Fix for @tonkmr review
First unfinished draft of intro rewrite focusing on the website rather
than phase field.

@@
 Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
-Potentials Repository (IPR~\cite{}) and on a larger scale the NIH
-Genetic Sequence Database (GenBank~\cite{}). In this work, we present
-a description of a generic web portal that leverages existing online
-services to provide a framework that may be adopted by other
-scientific communities. The first deployment of the PFHub framework
-supports phase-field practitioners and code developers participating
-in an effort to improve quality assurance for phase-field codes.
+Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
+the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
+work, we present a description of a generic web portal that leverages
+existing online services to provide a framework that may be adopted by
+other scientific communities. The first deployment of the PFHub
+framework supports phase-field practitioners and code developers
+participating in an effort to improve quality assurance for
+phase-field codes.
 
@@
 
-\section*{Introduction}
+\section*{Introduction (new)}
+
+Small scientific communities do not often have the resources to build
+and host dedicated web infrastructure to support their varied content
+and data requirements. In particular, hosting and supporting a complex
+content management system (CMS) including web servers, web frameworks
+and databases requires a great deal of configuration and long term
+support and funding. Furthermore, a turnkey CMS solution may not meet
+requirements for a particular scientific group that may require arcane
+data formats, unusual data display and custom client-side automation.
+The PFHub effort, instead of focusing on the CMS tool, focuses on
+customizing and delivering the "client-side" requirements whilst
+delegating back-end functionality to external services and then
+integrate with those services' APIs. The PFHub current effort supports
+a community of phase field code developers.
+
+\section*{Introduction (old)}
 

### 2019-03-27 _publications/jors/paper.tex
Changes requested by Peter

@@
 
+This list is for contributors to the code base, but not those that
+have only uploaded output results to the website.
+
 1. Wheeler, Daniel; A, \githublink{wd15} \\
@@
 
-See the contributors list on GitHub~\cite{contributors}.
+Also, see the contributors list on GitHub~\cite{contributors}.
 
@@
 PRedictive Integrated Structural Materials Science (PRISMS Center) at
-University of Michigan.
+University of Michigan. PWV is grateful for the financial assistance
+under the award 70NANB14H012 from the National Institute of Standards
+and Technology as part of the Center for Hierarchical Materials Design
+(CHiMaD).
 

### 2019-03-27 _publications/jors/paper.tex
Changes for @tonkmr

@@
 PFHub: The Phase-Field Community Hub\\[\baselineskip]
-\url{https://pages.nist.gov/pfhub}
 
@@
 existing online services to provide a framework that may be adopted by
-other scientific communities. The first deployment of the PFHub
+other small scientific communities. The first deployment of the PFHub
 framework supports phase-field practitioners and code developers
@@
 
-Small scientific communities do not often have the resources to build
-and host dedicated web infrastructure to support their varied content
-and data requirements. In particular, hosting and supporting a complex
-content management system (CMS) including web servers, web frameworks
-and databases requires a great deal of configuration and long term
-support and funding. Furthermore, a turnkey CMS solution may not meet
-requirements for a particular scientific group that may require arcane
-data formats, unusual data display and custom client-side automation.
-The PFHub effort, instead of focusing on the CMS tool, focuses on
-customizing and delivering the "client-side" requirements whilst
-delegating back-end functionality to external services and then
-integrate with those services' APIs. The PFHub current effort supports
-a community of phase field code developers.
+Generally, small scientific communities do not have the resources to
+build and host dedicated web infrastructure to support their varied
+content and data requirements. In particular, hosting and supporting a
+complex content management system (CMS) including web servers, web
+frameworks and databases requires a great deal of configuration and
+long term support and funding. Furthermore, a turnkey CMS solution may
+not meet requirements for a particular scientific group that may
+require arcane data formats, custom data displays and client-side
+automation. The PFHub effort, instead of focusing on the CMS tool,
+focuses on customizing and delivering the "client-side" requirements
+whilst delegating back-end functionality to external services that
+provide dependable APIs~\cite{cmsfree}.
 
-\section*{Introduction (old)}
+PFHub is a community effort spearheaded by the Center for Hierarchical
+Materials Design at Northwestern University and the National Institute
+of Standards and Technology in support of phase-field code
+development. The current PFHub deployment~\cite{pfhub} focuses on
+improving cross-collaboration between phase-field code developers and
+practitioners by providing a standardized set of benchmark
+problems~\cite{bm1, bm2} and a workflow for uploading and comparing
+benchmark results from different phase-field codes (\emph{e.g.},
+MOOSE~\cite{moose}, PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
+MMSP~\cite{mmsp}).
 
-The phase-field method (PFM) describes material interfaces at the
-mesoscopic scale between atomic scale models and macroscale models.
-The PFM is well established and there are an assortment of code
-frameworks (\emph{e.g.}, MOOSE~\cite{moose},
-PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
-MMSP~\cite{mmsp}) available for
-solving the wide variety of mesoscale phenomena (\emph{e.g.},
-dendritic growth, spinodal decomposition, grain growth). However,
-phase-field research groups often develop codes in isolation and do
-not support or distribute the code bases to the wider community. PFHub
-is a community effort spearheaded by the Center for Hierarchical
-Materials Design at Northwestern University and the National Institute
-of Standards and Technology to support the development of phase-field
-codes. In particular, the PFHub effort focuses on improving
-cross-collaboration between phase-field code developers and
-practitioners by providing a standardized set of benchmark
-problems~\cite{bm1, bm2} along with a web framework for uploading and
-comparing benchmark results from different codes.
+This paper presents the first deployment of the PFHub framework
+including its ``client-side'' focused design, how it employs external
+services and meta-data about the code base.
 
@@
 Jekyll static website generator~\cite{jekyll} along with automated
-frontend processing to eliminate the need for content management
-systems~\cite{cmsfree}, which are generally costly to maintain
-especially for small scientific communities with limited funding and
-staffing.
+front-end processing to eliminate the need for a CMS~\cite{cmsfree},
+which are generally costly to maintain especially for small scientific
+communities with limited funding and staffing.
 

### 2019-03-27 _publications/jors/paper.tex
Extend the intro

@@
 
-\section*{Introduction (new)}
+\section*{Introduction}
 
@@
 automation. The PFHub effort, instead of focusing on the CMS tool,
-focuses on customizing and delivering the "client-side" requirements
+focuses on customizing and delivering the client-side requirements
 whilst delegating back-end functionality to external services that
@@
 This paper presents the first deployment of the PFHub framework
-including its ``client-side'' focused design, how it employs external
-services and meta-data about the code base.
+including its client-side focused design, how it employs external
+services and meta-data about the code base. The paper describes the
+relative ease with which other scientific groups might adapt the
+framework for their own purposes and deploy using the fully
+reproducible Nix environment~\cite{nix}.
 

### 2019-03-27 _publications/jors/paper.tex
Changes for @amjokisaari

@@
 long term support and funding. Furthermore, a turnkey CMS solution may
-not meet requirements for a particular scientific group that may
-require arcane data formats, custom data displays and client-side
-automation. The PFHub effort, instead of focusing on the CMS tool,
-focuses on customizing and delivering the client-side requirements
-whilst delegating back-end functionality to external services that
-provide dependable APIs~\cite{cmsfree}.
+not meet requirements for most scientific communities that often use
+arcane data formats and require custom data displays along with
+client-side automation. The PFHub effort, instead of focusing on the
+CMS tool, focuses on customizing and delivering the client-side
+requirements whilst delegating back-end functionality to external
+services that provide dependable APIs~\cite{cmsfree}.
 
@@
 
-The PFHub website provides a facility for uploading, displaying and
-comparing results from the benchmark problems. The website uses the
-Jekyll static website generator~\cite{jekyll} along with automated
-front-end processing to eliminate the need for a CMS~\cite{cmsfree},
-which are generally costly to maintain especially for small scientific
-communities with limited funding and staffing.
+The PFHub framework provides a template for other small scientific
+communities to host custom content and integrate data from members of
+their community. The current deployment provides a facility for
+uploading, displaying and comparing results from benchmark problems
+supporting phase-field code developers and practitioners. However, the
+framework and overall philosophy are broadly transferable to other
+communities with some custom configuration and content generation. The
+framework uses the Jekyll~\cite{jekyll} static website
+generator~\cite{jekyll} along with automated front-end processing to
+eliminate the need for a CMS~\cite{cmsfree}, which is generally costly
+to maintain especially for small scientific communities with limited
+funding and staffing.
 
@@
   \item The users are first required to upload simulation outputs to
-    an archival resource (\emph{e.g.}, Figshare~\footnote{Certain
-      commercial equipment, instruments, or materials (or suppliers,
-      or software, ...) are identified in this paper to foster
-      understanding. Such identification does not imply recommendation
-      or endorsement by the National Institute of Standards and
-      Technology, nor does it imply that the materials or equipment
-      identified are necessarily the best available for the
-      purpose.\label{disclaimer}}) configured with permissive
-    cross-origin resource sharing (CORS).
+    an archival resource (\emph{e.g.},
+    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
+      instruments, or materials (or suppliers, or software, ...) are
+      identified in this paper to foster understanding. Such
+      identification does not imply recommendation or endorsement by
+      the National Institute of Standards and Technology, nor does it
+      imply that the materials or equipment identified are necessarily
+      the best available for the purpose.\label{disclaimer}})
+    configured with permissive cross-origin resource sharing (CORS).
   \item The metadata summarizing each simulation is entered into a
@@
 
-The benchmark specifications consist of equations, narrative, plots
-and code samples, and are composed in Jupyter Notebooks. The Jupyter
-Notebooks are included as static objects in the website after
-translation into HTML using the nbconvert tool~\cite{jupyter}.
+The current deployment of PFHub has benchmark specifications
+consisting of equations, narrative, plots and code samples, and are
+composed in Jupyter Notebooks. The Jupyter Notebooks are included as
+static objects in the website after translation into HTML using the
+nbconvert tool~\cite{jupyter}. There are currently 7 benchmark
+problems each with a number of variations. At the time of writing
+there are 108 separate benchmark result uploads~\cite{pfhub}, which
+have all been approved via pull-request for compatibility with the
+website.
 
@@
 archives avoids the complexity and administrative overhead of
-maintaining a live database and associated back-end application. The
-PFHub infrastructure provides a template for other small scientific
-communities to host custom content and integrate data from members of
-their community.
+maintaining a live database and associated back-end application.
 
@@
 The framework has a fully automated test recipe deployed on Travis CI
-with an environment built using the Nix Package
-Manager~\cite{nix}. The environment is pinned to a specific version of
-the Nixpkgs repository ensuring fully reproducible build and test
-phases as well as ensuring that the development and automated testing
+with an environment built using the Nix Package Manager~\cite{nix}. A
+fully automated test environment using continuous integration allows
+all developers and users to have common feedback on code updates and
+determine the compatibility of result uploads with the deployed
+website. The environment is pinned to a specific version of the
+Nixpkgs repository ensuring fully reproducible build and test phases
+as well as ensuring that the development and automated testing
 environments are identical. The full test recipe is outlined in a
@@
 streamlined deployment without the need for any back-end
-infrastructure.
+infrastructure and, thus, largely platform independent. For
+development purposes, a Nix installation is required or use of the
+supplied Docker container if using Windows.
 
@@
 \begin{itemize}
-  \item Upload new benchmark definitions in a format that Jekyll can
-    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
+  \item Upload new data upload specficiations (e.g. the phase-field
+    benchmarks in the PFHub website~\cite{pfhub}) in a format that
+    Jekyll can parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
   \item Edit the \texttt{benchmarks.yaml} file to reflect the new

### 2019-03-27 _publications/jors/paper.tex
Update reuse potential section
More cleanup

@@
 
-The website infrastructure can be cloned as a Git repository or
-downloaded as a ZIP archive and deployed with minimum effort. The
+The PFHub framework can be readily adopted by other communities that
+want to follow a CMS-free philosophy and use well supported external
+services. The website infrastructure can be cloned as a Git repository
+or downloaded as a ZIP archive and deployed with minimum effort. The
 mechanism for uploading data using Staticman can be easily configured
@@
 \begin{itemize}
-  \item Upload new data upload specficiations (e.g. the phase-field
-    benchmarks in the PFHub website~\cite{pfhub}) in a format that
-    Jekyll can parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
+  \item Upload new data upload specifications (\emph{e.g.} the
+    phase-field benchmarks in the PFHub website~\cite{pfhub}) in a
+    format that Jekyll can parse, \emph{e.g.}, Jupyter Notebook,
+    Markdown or HTML.
   \item Edit the \texttt{benchmarks.yaml} file to reflect the new

### 2019-03-27 _publications/jors/paper.tex
Remove new para before and after itemize list

@@
 Figure~\ref{fig:pfhub_website}.
-
 \begin{itemize}
@@
 \end{itemize}
-
 A combination of Jekyll templates and Coffeescript are used to access

### 2019-03-27 _publications/jors/paper.tex
Fix spelling

@@
 collate scientific results. Examples of such portals include the
-Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
+Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Interatomic
 Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale

### 2019-04-03 _publications/jors/paper.tex
Fix spellings

--- 2019-03-27 _publications/jors/paper.tex
@@
-%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.
+%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham University, UK.
 
@@
 collate scientific results. Examples of such portals include the
-Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
+Micromagnetic Modeling Group ($\mu$MAG~\cite{mumag}), the Interatomic
 Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale

### 2019-04-04 _publications/jors/paper.tex
Coffeescript -> CoffeeScript

@@
 \end{itemize}
-A combination of Jekyll templates and Coffeescript are used to access
+A combination of Jekyll templates and CoffeeScript are used to access
 and download the data links in the submitted YAML files and then
@@
     HTMLProofer~\cite{htmlproofer}.
-  \item Lint and test front-end Coffeescript using appropriate tools.
+  \item Lint and test front-end CoffeeScript using appropriate tools.
   \item Display a temporary version of the website using

### 2019-04-04 _publications/jors/paper.tex
Fix for tkphd

@@
 
-\usepackage{biblatex}
+\usepackage[sorting=none]{biblatex}
 \usepackage{hyperref}
@@
 \usepackage{hyperref}
+\usepackage{textcomp}
 
@@
 2. Keller, Trevor; A\\
-3. DeWitt, Stephen J.; E\\
-4. Jokisaari, Andrea M.; D\\
-5. Schwen, Daniel; D\\
+3. DeWitt, Stephen J.; B\\
+4. Jokisaari, Andrea M.; C\\
+5. Schwen, Daniel; C\\
 6. Guyer, Jonathan E.; A\\
-7. Aagesen, Larry; D\\
-8. Heinonen, Olle G.; B\\
-9. Tonks, Michael R.; G\\
-10. Voorhees, Peter W.; C\\
-11. Warren, James A.; F
+7. Aagesen, Larry; C\\
+8. Heinonen, Olle G.; D\\
+9. Tonks, Michael R.; E\\
+10. Voorhees, Peter W.; F\\
+11. Warren, James A.; G
 
@@
 
-B. Argonne National Laboratory, \\
+B. Materials Science and Engineering Department, \\
+University of Michigan, \\
+Ann Arbor, MI 48109 USA
+
+C. Fuel Modeling and Simulation Department, \\
+Idaho National Laboratory, \\
+Idaho Falls, ID 83415 USA
+
+D. Argonne National Laboratory, \\
 Lemont, IL 60439 USA
 
-C. Department of Materials Science and Engineering, \\
+E. Department of Materials Science and Engineering, \\
+University of Florida, \\
+Gainesville, FL 32611
+
+F. Department of Materials Science and Engineering, \\
 Northwestern University, \\
@@
 
-D. Fuel Modeling and Simulation Department, \\
-Idaho National Laboratory, \\
-Idaho Falls, ID 83415 USA
-
-E. Materials Science and Engineering Department, \\
-University of Michigan, \\
-Ann Arbor, MI 48109 USA
-
-F. Material Measurement Laboratory Office, \\
+G. Material Measurement Laboratory Office, \\
 Material Measurement Laboratory, \\
@@
 Gaithersburg, MD 20899 USA
-
-G. Department of Materials Science and Engineering, \\
-University of Florida, \\
-Gainesville, FL 32611
 
@@
 collate scientific results. Examples of such portals include the
-Micromagnetic Modeling Group ($\mu$MAG~\cite{mumag}), the Interatomic
+Micromagnetic Modeling Group (\textmu MAG~\cite{mumag}), the Interatomic
 Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale

### 2019-04-05 _publications/jors/paper.tex
Update for tkphd review

@@
 benchmark results from different phase-field codes (\emph{e.g.},
-MOOSE~\cite{moose}, PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
-MMSP~\cite{mmsp}).
+FiPy~\cite{fipy}, MMSP~\cite{mmsp}, MOOSE~\cite{moose},
+PRISMS-PF~\cite{prisms-pf}).
 
@@
 communities with some custom configuration and content generation. The
-framework uses the Jekyll~\cite{jekyll} static website
-generator~\cite{jekyll} along with automated front-end processing to
-eliminate the need for a CMS~\cite{cmsfree}, which is generally costly
-to maintain especially for small scientific communities with limited
-funding and staffing.
+framework uses the Jekyll static website generator~\cite{jekyll} along
+with automated front-end processing to eliminate the need for a
+CMS~\cite{cmsfree}, which is generally costly to maintain especially
+for small scientific communities with limited funding and staffing.
+The framework relies on the API, WebSocket and webhook infrastructure
+that underpins the modern web and allows external services to have
+full-duplex communication between servers and browsers. In particular,
+PFHub relies on GitHub's well maintained API and webhook functionality
+for external services (such as Travis CI~\cite{travis} and
+Staticman~\cite{staticman}).
 
@@
 Figure~\ref{fig:pfhub_website}.
-\begin{itemize}
+\begin{enumerate}
   \item The users are first required to upload simulation outputs to
-    an archival resource (\emph{e.g.},
-    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
-      instruments, or materials (or suppliers, or software, ...) are
-      identified in this paper to foster understanding. Such
-      identification does not imply recommendation or endorsement by
-      the National Institute of Standards and Technology, nor does it
-      imply that the materials or equipment identified are necessarily
-      the best available for the purpose.\label{disclaimer}})
-    configured with permissive cross-origin resource sharing (CORS).
+    an archival resource (\emph{e.g.}, Figshare\footnote{Certain
+      commercial equipment, instruments, or materials (or suppliers,
+      or software, ...) are identified in this paper to foster
+      understanding. Such identification does not imply recommendation
+      or endorsement by the National Institute of Standards and
+      Technology, nor does it imply that the materials or equipment
+      identified are necessarily the best available for the
+      purpose.\label{disclaimer}}~\cite{figshare}) configured with
+    permissive cross-origin resource sharing (CORS).
   \item The metadata summarizing each simulation is entered into a
@@
   \item Upon submission, the Staticman app~\cite{staticman} submits
-    the entered metadata as a GitHub pull request to the PFHub GitHub
-    repository.  The metadata is stored in a YAML file with a unique
-    path in the repository.
+    the entered metadata as a pull request aagainst the PFHub
+    repository hosted by GitHub. The metadata is stored in a YAML file
+    with a unique path in the repository.
   \item Travis CI~\cite{travis} performs linting on the submission and
@@
     compatible with GitHub Pages.
-\end{itemize}
+\end{enumerate}
 A combination of Jekyll templates and CoffeeScript are used to access
@@
 problems each with a number of variations. At the time of writing
-there are 108 separate benchmark result uploads~\cite{pfhub}, which
-have all been approved via pull-request for compatibility with the
-website.
+there are 108 separate benchmark result uploads~\cite{pfhub} submitted
+as pull requests and approved following code review to ensure
+compatibility with the website.
 
@@
 determine the compatibility of result uploads with the deployed
-website. The environment is pinned to a specific version of the
-Nixpkgs repository ensuring fully reproducible build and test phases
-as well as ensuring that the development and automated testing
-environments are identical. The full test recipe is outlined in a
-\texttt{.travis.yml} file stored in the repository~\cite{travisyml}
-and consists of the following steps.
+website. The environment is pinned to a specific version of the Nix
+Packages Collection (Nixpkgs~\cite{nixpkgs}), ensuring fully
+reproducible build and test phases as well as ensuring that the
+development and automated testing environments are identical. The full
+test recipe is outlined in a YAML file, \texttt{.travis.yml}, file
+stored in the repository~\cite{travisyml} and consists of the
+following steps.
 
-\begin{itemize}
-  \item Build the Nix environment from a cached storage reducing the
-    build time.
+\begin{enumerate}
+  \item Build the Nix environment from a persistent cache on Travis
+    CI, reducing the build time.
   \item Run automated tests on Jupyter Notebooks using
@@
     Surge~\cite{surge} for visual review.
-\end{itemize}
+\end{enumerate}
 
@@
 streamlined deployment without the need for any back-end
-infrastructure and, thus, largely platform independent. For
-development purposes, a Nix installation is required or use of the
-supplied Docker container if using Windows.
+infrastructure and, thus, is largely platform independent. For
+development purposes, a local installation of either Nix (on Linux or
+Mac) or Docker (on Linux, Mac or Windows) is required.
 
@@
 website for a particular scientific community would require
-considerable effort. The following steps are the more challenging
+considerable effort. The current effort is closely integrated with
+GitHub, but future deployments could be modified to use other
+repository services such as GitLab or BitBucket.
+
+The following steps are the more challenging
 aspects of deploying the framework for a new community.
@@
 PRedictive Integrated Structural Materials Science (PRISMS Center) at
-University of Michigan. PWV is grateful for the financial assistance
-under the award 70NANB14H012 from the National Institute of Standards
-and Technology as part of the Center for Hierarchical Materials Design
-(CHiMaD).
+University of Michigan. P.W.V. is grateful for the financial
+assistance under the award 70NANB14H012 from the National Institute of
+Standards and Technology as part of the Center for Hierarchical
+Materials Design (CHiMaD).
 

### 2019-04-05 _publications/jors/paper.tex
Sort out preamble
Reorder contributor affils
spelling

@@
 \usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{textcomp}
+
 \bibliography{paper}
-
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{textcomp}
 
@@
   \item Upon submission, the Staticman app~\cite{staticman} submits
-    the entered metadata as a pull request aagainst the PFHub
+    the entered metadata as a pull request against the PFHub
     repository hosted by GitHub. The metadata is stored in a YAML file
@@
 2. Keller, Trevor; A, \githublink{tkphd} \\
-3. DeWitt, Stephen J.; E, \githublink{stvdwtt} \\
-4. Jokisaari, Andrea M.; D, \githublink{amjokisaari} \\
-5. Schwen, Daniel; D, \githublink{dschwen} \\
+3. DeWitt, Stephen J.; B, \githublink{stvdwtt} \\
+4. Jokisaari, Andrea M.; C, \githublink{amjokisaari} \\
+5. Schwen, Daniel; C, \githublink{dschwen} \\
 6. Guyer, Jonathan E.; A, \githublink{guyer} \\

### 2019-08-05 _publications/jors/paper.tex
Remake PDF
docs(publication): revise for reviewers' feedback
Implement minor revisions based on reviewer's feedback

@@
 6. Guyer, Jonathan E.; A\\
-7. Aagesen, Larry; C\\
+7. Aagesen, Larry K.; C\\
 8. Heinonen, Olle G.; D\\
@@
 collate scientific results. Examples of such portals include the
-Micromagnetic Modeling Group (\textmu MAG~\cite{mumag}), the Interatomic
-Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
-the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
-work, we present a description of a generic web portal that leverages
-existing online services to provide a framework that may be adopted by
-other small scientific communities. The first deployment of the PFHub
-framework supports phase-field practitioners and code developers
-participating in an effort to improve quality assurance for
-phase-field codes.
+Micromagnetic Modeling Group (\textmu MAG~\cite{mumag}), the
+Interatomic Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a
+larger scale the NIH Genetic Sequence Database
+(GenBank~\cite{genbank}). In this work, we present a description of a
+generic web portal that leverages existing online services to provide
+a framework that may be adopted by other small scientific
+communities. The first deployment of the PFHub framework supports
+phase-field practitioners and code developers participating in an
+effort to improve quality assurance for phase-field codes.
 
@@
 
+The phase field method (PFM) describes material interfaces at the
+mesoscopic scale between atomic scale models and macroscale
+models~\cite{MOELANS2008268}. The PFM is well established and there
+are an assortment of code frameworks (\emph{e.g.}, FiPy~\cite{fipy},
+MMSP~\cite{mmsp}, MOOSE~\cite{moose}, PRISMS-PF~\cite{prisms-pf})
+available for solving the wide variety of phenomena associated with
+phase field (e.g. dendritic growth, spinodal decomposition, grain
+growth)~\cite{tonks}. However, it is difficult for novice as well as
+seasoned phase field practitioners to asses the capability of codes
+for different phenomena without extensive prototyping and
+groundwork. PFHub aims to provide a low barrier for comparing code
+output data using a standard set of metrics.
+
 PFHub is a community effort spearheaded by the Center for Hierarchical
@@
 problems~\cite{bm1, bm2} and a workflow for uploading and comparing
-benchmark results from different phase-field codes (\emph{e.g.},
-FiPy~\cite{fipy}, MMSP~\cite{mmsp}, MOOSE~\cite{moose},
-PRISMS-PF~\cite{prisms-pf}).
+benchmark results from different phase-field codes.
+
+Community based scientific efforts often require web services to share
+and display data in unique ways between groups and institutions. These
+services are difficult to implement due to the groundwork required to
+investigate and prototype the many data-sharing and CMS tools
+available. The PFHub framework provides a template for other
+scientific projects beyond the phase field community. The method
+outlined in this paper of using static infrastructure coupled with
+small independent third party web services provides a flexible
+approach eliminating the initial prototyping and on-going maintenance
+required for new infrastructure, while allowing developers to focus on
+their unique front-end data views.
 
@@
 including its client-side focused design, how it employs external
-services and meta-data about the code base. The paper describes the
+services and metadata about the code base. The paper describes the
 relative ease with which other scientific groups might adapt the
@@
 communities to host custom content and integrate data from members of
-their community. The current deployment provides a facility for
-uploading, displaying and comparing results from benchmark problems
-supporting phase-field code developers and practitioners. However, the
-framework and overall philosophy are broadly transferable to other
-communities with some custom configuration and content generation. The
-framework uses the Jekyll static website generator~\cite{jekyll} along
-with automated front-end processing to eliminate the need for a
+their community. The current deployment (see
+Figure~\ref{fig:pfhub_frontpage}) provides a facility for uploading,
+displaying and comparing results from benchmark problems supporting
+phase-field code developers and practitioners. However, the framework
+and overall philosophy are broadly transferable to other communities
+with some custom configuration and content generation. The framework
+uses the Jekyll static website generator~\cite{jekyll} along with
+automated front-end processing to eliminate the need for a
 CMS~\cite{cmsfree}, which is generally costly to maintain especially
@@
   \item The metadata summarizing each simulation is entered into a
-    form on the website, including relevant details such as memory
-    usage, run time and links to the data archived in the first step.
+    form on the website (see Figure~\ref{fig:pfhub_upload}), including
+    relevant details such as memory usage, run time and links to the
+    data archived in the first step.
   \item Upon submission, the Staticman app~\cite{staticman} submits
@@
     repository hosted by GitHub. The metadata is stored in a YAML file
-    with a unique path in the repository.
+    with a unique path in the repository, see~\cite{upload_data} for
+    an example.
   \item Travis CI~\cite{travis} performs linting on the submission and
@@
 and download the data links in the submitted YAML files and then
-display the data in interactive plots on the website. The interactive
-plots are displayed using the Plotly JavaScript Graphing
+display the data in interactive plots on the website. CoffeeScript is
+a higher level language than JavaScript and, thus, more readable
+whilst also allowing programming in a more functional manner which
+makes data manipulation pipelines both more succinct and easier to
+understand. The interactive plots (see Figure~\ref{fig:pfhub_results})
+are displayed using the Plotly JavaScript Graphing
 Library~\cite{plotly} as it provides a programmable interface and
-requires minimal configuration.
+requires minimal configuration, see~\cite{display_data} for typical
+data displayed on the interactive plots.
 
@@
 problems each with a number of variations. At the time of writing
-there are 108 separate benchmark result uploads~\cite{pfhub} submitted
+there are 109 separate benchmark result uploads~\cite{pfhub} submitted
 as pull requests and approved following code review to ensure
@@
 \begin{figure}
+  \includegraphics[width=\textwidth]{pfhub_frontpage.png}
+  \caption{Front page of the current version of the deployed PFHub
+    website showing links to the wiki and upload pages. The hexbin
+    splash provides links to phase field papers and websites. This can
+    easily be modified with alternative links and images by editing a
+    YAML file.}  \centering
+  \label{fig:pfhub_frontpage}
+\end{figure}
+
+\begin{figure}
   \includegraphics[width=\textwidth]{pfhub_website.png}
@@
   \label{fig:pfhub_website}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{pfhub_upload.png}
+  \caption{The form used to enter simulation result metadata and then
+    upload to the repository via a GitHub pull request allowing the
+    data to be checked before pushing to the website.}  \centering
+  \label{fig:pfhub_upload}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{pfhub_results.png}
+  \caption{Results comparison page for benchmark 3 (Dendritic
+    Growth). The data for each upload is plotted asynchronously and the
+    page is not affected if a data link dies.}  \centering
+  \label{fig:pfhub_results}
 \end{figure}
@@
     HTMLProofer~\cite{htmlproofer}.
-  \item Lint and test front-end CoffeeScript using appropriate tools.
+  \item Lint and test front-end CoffeeScript using
+    Coffeelint~\cite{coffeelint} and Mocha~\cite{mocha}, respectively.
   \item Display a temporary version of the website using
@@
 The PFHub framework can be deployed on any platform supporting Nix,
-which includes all contemporary Linux and Mac OS X platforms. Since
-the framework is built with Jekyll and automated front-end processing,
-it can be deployed on GitHub's Pages infrastructure, which enables
+which includes all contemporary Linux and macOS platforms. Since the
+framework is built with Jekyll and automated front-end processing, it
+can be deployed on GitHub's Pages infrastructure, which enables
 streamlined deployment without the need for any back-end
@@
 
-Currently, a deployment for a new community has not been attempted
-and, thus, the above steps need to be refined and documented.
+Further details on deployment and development of PFHub can be found in
+the development guide~\cite{development_guide}.  Currently, a
+deployment for a new community has not been attempted and, thus, the
+above steps need to be refined and documented.
 
